---
title: "Golf Ball"
author: "Author"
date: "04/07/2019"
output:
  github_document:
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    fig_caption: yes
    number_sections: yes
    pdf_document: default
    toc: yes
    toc_depth: '1'
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 1
  word_document:
    toc: yes
    toc_depth: '1'
    
---
#OBJECTIVE

At the 0.05 level of significance, is there a evidence of a difference in the mean distances travelled by the golf balls with different designs?

```{r}
mydata=read.csv("Golfball.csv")
```

```{r}
attach(mydata)
dim(mydata)
```
Inference:
There are 40 rows and 2 columns in the given dataset
```{r}
str(mydata)
```
Inference: 
Given that there are four levels of design namely, design1,design2,design3 and design4
```{r}
summary(mydata)
```

```{r}
library(psych)
describeBy(Distance,group=Design)
```
```{r}
library(lattice)
histogram(~Distance|Design)
```

```{r}
boxplot(Distance~Design,horizontal=TRUE,col=c("Red","Blue","Green","Yellow"))
```
Inference:
Boxplot indicates that there are no outliers
```{r}
Model=aov(Distance~Design,data=mydata)
Model
```

```{r}
summary(Model)
```
Inference:
F value is 53.03 which is good, and p value is less than 0.05, indicating there are differences in the mean distance travelled by the golf balls with different designs.
```{r}
# To investigate further we need to do a Tukey test
tuk<-TukeyHSD(Model)
tuk
```

```{r}
plot(tuk)
```

Inference:
Design 4 and Design 3 shows significance with a p value of 0.72 and others does not show any form of significance.